\section{Introduction}%
\label{sec:introduction}%
% 
\ac{DUS} is one of the safest forms of medical imaging and has become
ubiquitous in clinical practice. However it has been demonstrated to
cause \ac{LH} in a variety of mammals. While the problem does not
appear to be one of medical concern under typical clinical conditions,
the underlying physical mechanism is not well understood and more
information is needed. 

Over the last few decades \ac{DUS}-induced \ac{LH} has been studied
extensively and is the only known bioeffect of non-contrast, pulsed
\ac{US} known to occur in mammals under clinically relevant
conditions. While it has been not been directly demonstrated in
humans, it has been shown to occur in a variety of mammals including
mice, rats, rabbits, pigs, and monkeys
\citep{Child1990,OBrien2006a,Tarantal1994a,Miller2012}.
\ac{DUS}-induced \ac{LH} does not appear to be caused by traditionally
expected \ac{US} bioeffects mechanisms. Typically, \ac{US} bioeffects
mechanisms are classified as thermal or non-thermal with the bulk of
non-thermal bioeffects being a result of acoustic
\ac{IC}. \cite{Zachary2006} finds that \ac{DUS}-induced lung lesions
are different from induced by heat and concludes that thermal
mechanisms are not likely to be the cause. \cite{OBrien2000} observes
that the severity of \ac{DUS}-induced \ac{LH} in mice increases under
raised hydrostatic pressure, and \cite{Raeman1996} finds that the
\ac{LH} is unaffected by the introduction of \ac{US} contrast
agents. Both of these findings are inconsistent with \ac{IC}-induced
hemorrhage. One study reports detecting cavitation during
\ac{DUS}-lung interaction in rats \cite{Holland1996}. \cite{Tjan2007}
consider another potential damage mechanism, that focused \ac{US} may
lead to the ejection of droplets capable of puncturing the air-filled
sacs within the lung. To investigate this, they a develop
potential-flow solution for an inviscid, free surface subjected to a
Gaussian velocity potential and show that the proposed droplet
ejection may occur under certain circumstances. \cite{Simon2012}
observed \ac{HIFU} induced atomization of tissue at air
interfaces. Other studies have used experiments and nonlinear modeling
to look at possible nonlinear effects of ultrasound in
tissue. \cite{Khokhlova1997} used spectral methods to model
propagation of plane waves in soft tissue to study nonlinear
attenuation and wave propagation during
\ac{HIFU}. \cite{Khokhlova2005} numerically solved a KZK-type equation
to simulate the \ac{HIFU} field in a tissue phantom with the purpose
of studying the impact of nonlinear phenomena on lesion formation.
Despite these efforts, the precise damage mechanism underlying
\ac{DUS}-induced \ac{LH} is still unknown. The aim of this work is to
investigate a possible physical mechanism for \ac{DUS}-induced
\ac{LH}. 

The proposed damage mechanism is based on the idea that acoustic waves
are capable generating baroclinic vorticity at a perturbed fluid-fluid
interface, which is capable of then driving the interface to
deform. There has been extensive research into the fundamental physics
describing interactions between mechanical waves, acceleration, and
fluid-fluid interfaces. Much of this research is motivated by
applications in fusion energy and astrophysics and accordingly has
sought to investigate regimes outside of those of acoustic
interests. \cite{Taylor1950} predicted that for an interface between
two fluids of different density, if the fluid was accelerated normal
to the interface in the heavy-to-light direction, perturbations at the
interface would grow. That is to say that a ``bubble'' of light fluid
penetrates the heavy fluid, and a ``spike'' of heavy fluid penetrates
the light fluid. This is known as the \ac{RTI}. A similar topic of
past study is the \ac{RMI}, which occurs when a perturbed fluid-fluid
interface is instantaneously accelerated by a shock, causing the
interface perturbation to grow \citep{Brouillette2002,Drake2006}. This
growth is driven by a sheet of baroclinic vorticity deposited along
the interface as a result of misalignment between the pressure
gradient across the shock and the density gradient across the
perturbed interface. This physical mechanism by which these misaligned
gradients create a torque on fluid particles and generate vorticity
can be thought of in terms of a hydrostatic balance upon a
particle. Pressure gradients result in acceleration of the flow that
is inversely proportional to density. When these two gradients are
misaligned, the result is a shearing effect on the fluid and vorticity
is generated. A graphical explanations of baroclinic vorticity
generation and the resulting interface deformation can be found in
\citep{Heifetz2015}. Analytically, baroclinic vorticity generation can
be shown by taking the curl of the conservation of momentum equation
for a compressible fluid. However we note that it is a nonlinear
effect and cannot be explained by traditional linear acoustics.

The physics of the \ac{RMI} are fairly well understood. For the
classical \ac{RMI} setup a planar shock impinges normally upon the
peaks and troughs of a sinusoidal interface. The interface is
accelerated non-uniformly counter-rotating vorticies are generated
across the interface. This drives peaks and troughs of the interface
to accelerate in the opposite direction. Much like in the case of the
\ac{RTI} instability, this too results in light fluid penetrating the
heavy fluid and vice versa. For the case of a wave moving from a light
fluid into a heavy one, the peaks and troughs of the interface
accelerate away from one another, growing the interface perturbation
perturbation. For the case of a wave moving from a heavy fluid to a
lighter fluid, the peaks and troughs interface initially accelerate
toward one another. They then pass each, inverting the phase of the
interface perturbation, and continue moving in opposite directions,
growing the perturbation amplitude.

Previous studies of the \ac{RMI} have utilized theory, computation,
and experiments to describe the behavior of the interface after the
wave has passed. \cite{Richtmyer1960} performed the linear stability
perturbation analysis developed by \cite{Taylor1950} for the case of
an impulsive acceleration to create a model for the initial growth of
the interface perturbation. \cite{Meshkov1969} experimentally
confirmed Richtmyer's qualitative predictions, hence the name of the
instability. \cite{Meyer1972} performed numerical simulations of the
\ac{RMI} and found good agreement with Richtmyer for the case of a
shock impinging upon a light-heavy interface. \cite{Fraley1986} used
Laplace transforms in order to find the first analytical solution for
the asymptotic growth rate for a shocked interface between perfect
gases. To describe the late time, nonlinear growth of the
perturbation, \cite{Zhang1997} used single mode perturbation, keeping
many high order terms, to describe the velocity of the bubble and
spike regions of the fluid. \cite{Sadot1998} combined the linear,
impulsive solution with potential flow models of the asymptotic
behavior of the bubble and spike to develop a model for the
perturbation growth that is in good agreement with shock tube
experiments for shocks with Mach numbers Ma=1.3, 3.5. Vortex theory
has also been used to describe the behavior of the
interface. \cite{Jacobs1996} horizontally oscillated a container with
two vertically stratified liquids to obtain standing waves and then
bounced the container off of a coil spring to study the incompressible
\ac{RMI}. The late time evolution of is interface is modeled using a
row of line vorticies to obtain qualitatively similar results to those
experimentally observed, however the late-time growth rate is
underestimated. \cite{Samtaney1994} used shock polar analysis to find
the circulation deposited by a shock on planar and non-planar
interfaces. Their results are validated using and Euler code and found
to be within 10\% of the computed value for $1.0\,<\,$Ma$\,\leq\,1.32$
for all $\rho_2/\rho_1\,>\,1$, and
$5.8\,\leq\,\rho_2/\rho_1\,\leq\,32.6$ for all Ma.

Computational and experimental approaches has been used to study the
impact of nonlinear effects on wave-interface problems such as
shock-bubble and shock-droplet interactions. \cite{Haast1987}
experimentally shocked helium and R22-filled bubbles in air, and
showed that transmitted waves overtook one another an merged
downstream as a result of nonlinear gas dynamics. Numerical
simulations simulations of shock-bubble interactions have verified the
timescales and physical features observed in these experiments. These
simulations, in conjunction with nonlinear theory, and have shown that
baroclinic vorticity is generated by the wave-interface interaction,
and dominates the late-time dynamics of the system
\citep{Picone1988,Quirk2006}. \cite{Hawley1989} performed numerical
experiments to demonstrate that a vorticity deposition and evolution
can be used to explain the dynamics of shock-accelerated fluid-fluid
interfaces after early times. We argue that the basic problem setup of
the \ac{RMI}, a mechanical wave impinging upon a fluid-fluid
interface, is physically similar the an acoustic wave interactions
with air-tissue interfaces in the lungs. While the pressure gradients
of acoustic waves are much weaker than those of shock waves,
nonlinearity arises from the strong density discontinuity across the
tissue-air interfaces of the lungs.

The objective of the present study is to provide a detailed
explanation of the physics governing a perturbed water-air interface
driven by a trapezoidal acoustic wave. This separate from previous
research, which has largely looked at constantly-accelerated and
shock-accelerated interfaces. Consequently, there are physically novel
aspects of the present study.  First, acoustic waves, which are
typically thought of as small amplitude are shown to drive
perturbation growth at the interface via baroclinic vorticity. Shock
waves are, by definition, discontinuous and hence their propagation is
a nonlinear process. In contrast, the propagation of acoustic waves in
a homogeneous medium is a linear process. In the present study
nonlinearity occurs as a result of the strong density discontinuity at
the liquid-gas interface. Second, the acoustic wave has a finite
duration. Hence the vorticity is deposited throughout a finite
interaction time, unlike in the case of the \ac{RMI} in which it is
created by an instantaneous acceleration or the \ac{RTI} in which
vorticity results from constant acceleration. Unlike shocks, which
occur over a few molecular mean free paths and interact nearly
instantaneously, acoustic waves occupy a finite space. Hence their
interaction with interfaces occurs over a finite time. And third,
interface deformation that occurs during the acoustic wave-interface
interaction cannot be neglected. Transient interactions between
deforming interfaces and multiple shocks are known to be capable of
affecting the long term growth of the
interface. \cite{HenrydeFrahan2015b} demonstrated that interface
growth could be controlled through transient wave-interface
interactions by simulating shock passage through layered media, as a
result of subsequent interactions between the interfaces and reflected
and transmitted shocks and rarefactions. This work demonstrates that
interface deformations that occur during the interaction with the
acoustic wave can have a strong effect on the final growth of the
interface.

In the remainder of this work we will first present a model problem
and a set of numerical experiments designed to investigate the
fundamental physics underlying interactions between acoustic waves and
perturbed interfaces between fluids. We will present results that
specifically explore the dependence of the interface dynamics on
acoustically relevant properties including the amplitude and
wavelength of the acoustic wave. We pay particular attention to the
finite duration of the wave-interface interaction, and the interface
deformation that occurs during this period. We perform analysis to
explain the vorticity deposition and late time behavior of the
interface after all acoustic waves have passed. The results will be
discussed to address the following questions:

We will then discuss on the significance of these results as
they regard to the motivating problem of \ac{DUS}-induced lung
hemorrhage. We will finally end by summarizing the main conclusions
drawn from this work and suggest the next steps to be taken.


% \begin{figure}[h]
%   \centering
%   \def\svgwidth{0.48\textwidth}
%   \import{./figs/lung_figs/}{usbe_lung_schematic2.pdf_tex} \hfill%
%   \caption[A schematic view of the model problem]{A schematic of an
%     ultrasound wave impinging from tissue onto an air-filled alveolus.}
%   \label{fig:problem_schematic}
% \end{figure}

%
% \begin{comment} %This was too pedagogical for paper, but could be useful for thesis.
%   The physics of the \ac{RMI} are fairly well understood. For the
%   classical \ac{RMI} setup a planar shock impinges normally upon the
%   peaks and troughs of a sinusoidal interface. As the degree of
%   misalignment varies along the interface, the interface is
%   accelerated non-uniformly. The direction of the vorticity changes
%   where the slope of the interface changes. This counter rotation on
%   either side of interface peaks and troughs entrains nearby fluid
%   causing interface peaks to accelerate in one direction and troughs
%   to accelerate in the opposite direction. Much like in the case of
%   the \ac{RT} instability, this too results in light fluid penetrating
%   the heavy fluid and vice versa. How exactly this occurs varies
%   slightly depending on the relative densities of the two fluids. For
%   the case of a wave moving from a light fluid into a heavy one, the
%   peaks and troughs of the interface are initially accelerated to move
%   away from one another, and the interface perturbation amplitude
%   undergoes growth exclusively. For the case of a wave moving from a
%   heavy fluid to a lighter fluid, the peaks and troughs of the
%   interface are accelerated such that they initially move closer to
%   one another decreasing the perturbation amplitude. They then pass
%   one another, inverting the phase of the interface perturbation, and
%   then continue moving in opposite directions, growing the
%   perturbation amplitude. This process is illustrated in
%   \citep{Brouillette2002}.
%   \begin{comment}
%     \begin{figure}
%       \centering \def\svgwidth{0.9\textwidth}
%       \import{./figs/lung_figs/}{brouillette_fig3_mod.pdf_tex} \hfill%
%       \caption[A schematic view of the \ac{RMI} instability for a
%       heavy-light interface]{Adapted from \cite{Brouillette2002}. The
%         \ac{RMI} for a heavy-light interface is illustrated. The
%         initial condition (left), circulation post wave-interface
%         interaction (center), and perturbation growth (right) are
%         shown.}
%       \label{fig:rmi_schematic}
%     \end{figure}
%   \end{comment}
%   Previous studies of the \ac{RMI} have utilized theory, computation,
%   and experiments to describe the behavior of the interface after the
%   wave has passed. \cite{Richtmyer1960} performed the linear stability
%   perturbation analysis developed by \cite{Taylor1950} for the case of
%   an impulsive acceleration to create a model for the initial growth
%   of the interface perturbation. \cite{Meshkov1969} experimentally
%   confirmed Richtmyer's qualitative predictions, hence the name of the
%   instability. \cite{Meyer1972} performed numerical simulations of the
%   \ac{RMI} and found good agreement with Richtmyer for the case of a
%   shock impinging upon a light-heavy interface. \cite{Fraley1986} used
%   Laplace transforms in order to find the first analytical solution
%   for the asymptotic growth rate for a shocked interface between
%   perfect gases. To describe the late time, nonlinear growth of the
%   perturbation, \cite{Zhang1997} used single mode perturbation,
%   keeping many high order terms, to describe the velocity of the
%   bubble and spike regions of the fluid. \cite{Sadot1998} combined the
%   linear, impulsive solution with potential flow models of the
%   asymptotic behavior of the bubble and spike to develop a model for
%   the perturbation growth that is in good agreement with shock tube
%   experiments for shocks with Mach numbers Ma=1.3, 3.5. Vortex theory
%   has also been used to describe the behavior of the
%   interface. \cite{Jacobs1996} horizontally oscillated a container
%   with two vertically stratified liquids to obtain standing waves and
%   then bounced the container off of a coil spring to study the
%   incompressible \ac{RMI}. The late time evolution of is interface is
%   modeled using a row of line vorticies to obtain qualitatively
%   similar results to those experimentally observed, however the
%   late-time growth rate is underestimated. \cite{Samtaney1994} used
%   shock polar analysis to find the circulation deposited by a shock on
%   planar and non-planar interfaces. Their results are validated using
%   and Euler code and found to be within 10\% of the computed value for
%   $1.0\,<\,$Ma$\,\leq\,1.32$ for all $\rho_2/\rho_1\,>\,1$, and
%   $5.8\,\leq\,\rho_2/\rho_1\,\leq\,32.6$ for all Ma.
% \end{comment}




%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
