\chapter{Introduction to ultrasound bioeffects} \label{ch:usbe_intro}%
The purpose of this chapter is twofold. First, I provide a brief
introduction to ultrasound and related biological effects to provide
physical context for this work. Second, I offer a brief overview of
the work to be presented and its significance. For a more detailed
overview of the relevant literature, the reader is referred to later
parts of this document, and to this authors published works.

\section{Physical context} \label{sec:usbe_intro_physical_context}%
Diagnostic \ac{US} has proven to be among the safest and most powerful
medical imaging tools currently available \hl{CITE}. Its use has become
ubiquitous throughout modern medicine. The basic physical principle
underlying this technology is the scattering of sound at material
interfaces. In practice, high-frequency, typically MHz range, acoustic
waves and pulses are created at the surface of the body using a
piezoelectric \ac{US} transducer. These vibrations propagate via an
acoustic coupling medium from the transducer into the tissue and
scatter at changes in the material properties of the medium. More
simply, some of the sound echoes whenever it moves from one tissue to
another, or hits a cavity in the body. These echoes are then picked up
by a receiver and recorded. This echo signal is processed to obtain
real-time images of the scattering surface.

While clinical \ac{US} is typically safe there are specific instances
during which \ac{US} can interact with tissue in such a way that the
tissue is physically altered. These effects to the body are referred
to as \ac{US} bioeffects. Understanding these \ac{US}-tissue
interactions is important for the development of safe, effective
\ac{US} techniques \citep{Dalecki2004}. While the entire field of
therapeutic \ac{US} is focused on intentionally causing bioeffects in
a way that is beneficial to the patient, diagnostic \ac{US} is a
different story. Bioeffects that occur during diagnostic \ac{US}
typically take the form of unintended hemorrhage, tissue damage, or
cell death. Depending on the physical damage mechanism responsible,
these bioeffects are broadly classified into two groups, thermal and
non-thermal \citep{OBrien2007}. The first group, thermal bioeffects
are characterized by deposition of acoustic energy into tissue as heat
via viscous dissipation. At the cellular and molecular scales, this
can lead to the release of highly reactive free radicals, protein
denaturation, and ultimately tissue damage and death. Little else will
be said about thermal bioeffects, as the bioeffects problems of
interest to this work are a result of non-thermal mechanisms.

The bulk of known non-thermal bioeffects are attributed to
acoustically-induced cavitation. Acoustic cavitation is the phenomenon
by which gas nano and microbubbles, called cavitation nuclei, are
cyclically grown by low pressures within the \ac{US} field and then
collapsed high pressures within the field. Cavitation can be divided
into two categories, stable cavitation, also called gas body
activation, and \ac{IC}, formerly referred to as transient
cavitation. Stable cavitation typically occurs for low \ac{US}
intensity an is characterized by bubbles periodically oscillating
around an equilibrium radius for multiple acoustic cycles. \ac{IC}
typically occurs for higher ultrasound intensities. During \ac{IC} the
bubble dynamics during collapse are dominated by the inertia of the
surrounding fluid. The bubble collapses violently to a tiny fraction
of its original size and then explosively rebounds back. There are
variety of physical phenomena associated with \ac{IC} that may be
responsible for observed \ac{US} bioeffects. Upon collapse, the
pressure and temperature within the bubbles spike, often reaching
billions of pascals and thousands of Kelvin respectively. Due to the
pressure difference between the vapor/gas mixture within the bubble at
collapse and the surrounding media, the collapsed bubble can emit a
powerful shock wave. When cavitation is triggered near a rigid
surface, the bubble can collapse in a radially asymmetric fashion
causing a high speed ``re-entrant'' jet of liquid to impinge upon the
surface, effectively striking the surface with a liquid hammer. If
cavitation occurs at an appropriate distance from a non-rigid surface,
such as soft tissue boundaries and blood vessel walls, the jet can
impinge away from the surface, potentially invaginating the surface
\citep{Brujan2011}. One type of \ac{DUS} for which cavitation is of
particular concern is \ac{CEUS}, which uses contrast-agent
microbubbles injected into patients bloodstream to act as additional
scattering surfaces. These microbubbles can also serve as cavitation
nuclei and have been associated with a variety of \ac{US} bioeffects. 

\hl{
 MECHANICAL INDEX PARAGRAPH:} As a result of the potential for
  cavitation-related \ac{US} bioeffects the United States Food and
  Drug Administration called for a metric to predict likely cavitation
  damage from ultrasound. As bioeffects are typically attributed to
  \ac{IC}, efforts to predict cavitation damage considered the
  likelihood of \ac{IC} based on theoretical calculations of free gas
  bubbles in water. In the case of acoustic cavitation, this depends
  on the duration of peak negative pressure experienced by a
  cavitation nucleus, with longer interactions depositing more energy
  into the nucleus, and thus having a greater likelihood inducing
  \ac{IC}. The duration of the \ac{PRPA} is inversely related to the
  \ac{US} frequency. \cite{Holland1989} demonstrated that the
  threshold \ac{PRPA} needed to trigger \ac{IC}, defined based on a
  maximum bubble temperature $\geq5000$K, depended on the size of the
  cavitation nucleus. Smaller cavitation nucleii, must overcome
  greater surface tension effects in order to cavitate, with the
  Laplace pressure scaling inversely with the radius of the
  nucleus. Furthermore, as initial radius a nucleus increases, the
  inertia of the surrounding fluid that must be overcome also
  increases\cite{AiumS72000}. Thus \cite{Holland1989} illustrated that
  for a given frequency their is an optimal nucleus size for
  triggering \ac{IC}. Based on these calculations and corrections for
  heat dissipation in tissue the \ac{MI} was created as a measure of
  ultrasound induced cavitation related bioeffects and defined as 
  \begin{align}
    MI = \frac{P_{r.3}}{\sqrt{f_c}},
  \end{align}
  where $P_{r.3}$ is the \ac{PRPA} derated by $0.3$ dB/MHz-cm and
  $f_c$ is the center frequency \cite{Apfel1991}. The United States
  \ac{FDA} mandates that $MI\leq1.9$ for diagnostic imaging, though
  \ac{US} bioeffects have been observed at \ac{MI} below this in case
  of \ac{DUS} of mammalian lungs.


Another non-thermal \ac{US} bioeffect of interest is \ac{DUS}-induced
\ac{LH}, which is the only known bioeffect of non-contrast \ac{DUS}
known to occur in mammals. Despite the fact that this phenomenon was
first observed in mice over twenty years ago \citep{Child1990}, the
underlying physical damage mechanisms remain unknown. Research has
shown that thermal damage mechanisms are unlikely as \ac{DUS}-induced
lung lesions do not appear similar to those induced by heat
\citep{Zachary2006}. Furthermore, cavitation mechanisms do not appear
to be responsible, as the severity of \ac{DUS}-induced \ac{LH} in mice
increased under raised hydrostatic pressure \citep{OBrien2000} and was
unaffected by the introduction of \ac{US} contrast agents into
subjects. Both of these results are inconsistent with what is expected
of \ac{IC}-induced bioeffects. Works by \cite{Tjan2007,Tjan2008} model
the evolution of an inviscid, free surface subjected to a Gaussian
velocity potential and find that this can lead to the ejection of
liquid droplets. They go on to say that \ac{DUS} of the lung may
similarly lead to the ejected of droplets capable of puncturing the
air-filled sacs within the lung. This problem is central to the our
present and future work, and makes up the bulk of this proposal. As
such, a far more in-depth literature review will be provided in
Chapter \ref{ch:usbe_lung}.

\section{An overview the present work}
\label{sec:usbe_intro_overview}%
This dissertation focuses on two specific problems within the realm of
\ac{DUS}-related bioeffects and the underlying physics of
each. Specifically, we will consider contrast enhanced ultrasound and
\ac{DUS}-induced lung tissue.

First, in Chapter \ref{ch:usbe_bubble} we look at the problem of
contrast enhanced ultrasound and consider calculated cavitation
dynamics as they relate to experimentally observed bioeffects from
corresponding experiments. We present past work in which we simulate
ultrasonically induced cavitation of contrast agent microbubbles in
soft tissue \citep{Patterson2012}. We use experimentally measured
$1.5-7.5$ MHz \ac{US} waves, previously used by \cite{Miller2008b} to
determine kidney capillary hemorrhage threshold amplitudes in rats, as
input to the simulation. The calculated cavitation dynamics and
theoretical inertial cavitation thresholds \citep{Flynn1982,Apfel1982}
are compared with known thresholds for kidney hemorrhage to
investigate their dependence on US, gas, and tissue properties. At the
time of its publication, this work was unique in its combination of
experimental results and numerical modeling to approach this problem.

Second, in Chapter \ref{ch:usbe_lung} we consider \ac{DUS}-induced
\ac{LH} and the underlying physics of acoustically driven liquid-gas
interfaces. We propose acoustically-generated baroclinic vorticity as
a previously unconsidered damage mechanism. To investigate this, we
develop a model of \ac{DUS}-alveolus interaction as an acoustically
driven liquid-gas interface, which is representative of tissue-air
interfaces within the lungs. We perform numerical simulations to show
that the resulting vorticity at the interface, may be capable of
deforming the interface and thus straining fragile alveolar walls
within the lungs, possibly to the point of hemorrhage. We generalize
our discussion to acoustically-driven, perturbed, liquid-gas
interfaces. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../prelim"
%%% End:
